---
format: gfm
---

# BRFSS Assignment

This repo lightly cleans and samples from the Behavioral Risk Factor Surveillance System (**BRFSS**) Public Use File to create smaller, human friendly versions for students to easily work with.

```{r Setup}
if (!require("pacman")) {
  install.packages("pacman")
}

pacman::p_load(
  tidyverse,
  haven,
  janitor,
  here,
  readxl,
  here
)
```

### Primary functionality

There are two primary functions:

1.  `clean_brfss`: to clean the raw BRFSS file. Has four parts (1) read from SAS, (2) renames names to human-reabable names and (3) adds NA values where appropriate, and recodes variables from numeric to long-form values.

2.  `write_team_files`: to write clean files to `.xlsx` files for student teams. These files will end up in `/data/clean/`

```{r Example}
#| output: false

source(here::here("R", "clean_brfss.R"))

dat_brfss_clean <- clean_brfss()

# writes files for 10 teams of 10,000 rows each
write_team_files(
  data = dat_brfss_clean,
  n_teams = 10,
  n_rows = 10000,
  seed = 365
)
```

### Codebook
This repo also comes with two code books that are created (fairly manually) in the function `create_codebooks`. This should only be run if a variable is added or changed.